The \dealii{} Library, Version 8.5

### 2017-04-07 8.5/paper.tex
update date
remove marginpar
Add missing punctuation in affiliation addresses.

\author[9]{Bruno Turcksin\footnote{
  This manuscript has been authored by UT-Battelle, LLC under Contract No.
  DE-AC05-00OR22725 with the U.S. Department of Energy. The United States
  Government retains and the publisher, by accepting the article for
  publication, acknowledges that the United States Government retains a
  non-exclusive, paid-up, irrevocable, worldwide license to publish or reproduce
  the published form of this manuscript, or allow others to do so, for United
  States Government purposes. The Department of Energy will provide public
  access to these results of federally sponsored research in accordance with the
  DOE Public Access Plan (http://energy.gov/downloads/doe-public-access-plan).}}
\affil[9]{Computational Engineering and Energy Sciences Group,
  Computional Sciences and Engineering Division,
  Oak Ridge National Laboratory, 1 Bethel Valley Rd.,
  TN 37831, USA
  {\texttt{turcksinbr@ornl.gov}}}

\author[10]{David Wells}
\affil[10]{Department of Mathematical Sciences, Rensselaer Polytechnic Institute,
Troy, NY 12180, USA
  {\texttt{wellsd2@rpi.edu}}}

@@

\marginpar{Update date}
\dealii{} version 8.5.0 was released March 11, 2017. This paper provides an
overview of the new features of this release and serves as a citable
reference for the \dealii{} software library version 8.5. \dealii{} is an
object-oriented finite element library used around the world in the
development of finite element solvers. It is available for free under the
GNU Lesser General Public License (LGPL) from the \dealii{} homepage at
\url{http://www.dealii.org/}.

@@

In addition to tutorials, \dealii{} has a separate ``code gallery'' that
consists of programs shared by users as examples of what can be
done with \dealii{}. While not part of the release process, it is nonetheless
worth mentioning that the set of new programs since the last release covers
the following topics:
\marginpar{Add the muscle elasticity example if it is merged in time.}
  \begin{itemize}
    \item Quasi-static quasi-incompressible visco-elastic material behavior;
    \item Multiphase Navier-Stokes flow;
    \item The evolution of global-scale topography on planetary bodies;
    \item Goal-oriented elastoplasticity.
  \end{itemize}

>>>>

\author[9]{Bruno Turcksin\footnote{
  This manuscript has been authored by UT-Battelle, LLC under Contract No.
  DE-AC05-00OR22725 with the U.S. Department of Energy. The United States
  Government retains and the publisher, by accepting the article for
  publication, acknowledges that the United States Government retains a
  non-exclusive, paid-up, irrevocable, worldwide license to publish or reproduce
  the published form of this manuscript, or allow others to do so, for United
  States Government purposes. The Department of Energy will provide public
  access to these results of federally sponsored research in accordance with the
  DOE Public Access Plan (http://energy.gov/downloads/doe-public-access-plan).}}
\affil[9]{Computational Engineering and Energy Sciences Group,
  Computional Sciences and Engineering Division,
  Oak Ridge National Laboratory, 1 Bethel Valley Rd.,
  TN 37831, USA.
  {\texttt{turcksinbr@ornl.gov}}}

\author[10]{David Wells}
\affil[10]{Department of Mathematical Sciences, Rensselaer Polytechnic Institute,
Troy, NY 12180, USA.
  {\texttt{wellsd2@rpi.edu}}}

@@

\dealii{} version 8.5.0 was released April 6, 2017. This paper provides an
overview of the new features of this release and serves as a citable
reference for the \dealii{} software library version 8.5. \dealii{} is an
object-oriented finite element library used around the world in the
development of finite element solvers. It is available for free under the
GNU Lesser General Public License (LGPL) from the \dealii{} homepage at
\url{http://www.dealii.org/}.

@@

In addition to tutorials, \dealii{} has a separate ``code gallery'' that
consists of programs shared by users as examples of what can be
done with \dealii{}. While not part of the release process, it is nonetheless
worth mentioning that the set of new programs since the last release covers
the following topics:
%\marginpar{Add the muscle elasticity example if it is merged in time.}
  \begin{itemize}
    \item Quasi-static quasi-incompressible visco-elastic material behavior;
    \item Multiphase Navier-Stokes flow;
    \item The evolution of global-scale topography on planetary bodies;
    \item Goal-oriented elastoplasticity.
  \end{itemize}
